More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
update TODOs
proof in progress

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\end{mathpar}
such that\\
\begin{mathpar} 
s=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_m=s'
\\\\
\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred^3_i\subst{\Post^2})\subst{\Post^1_i}

@@

\begin{mathpar}
\Longleftrightarrow  \left \{ \begin{array}{l} 
\alpha = \tau \wedge  \vis{\overline{\beta^2}}=\emptyset \wedge \Pred^2 =\symb{True} \wedge \Post^2 =\symb{Id(s)}\\
\\
\bigvee \\
\\
{
\openrule
         {
           \overline{\gamma},
		\Pred,
				({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{array}
\right.
\end{mathpar}

\begin{proof} ($\Rightarrow$) We proceed by induction by induction the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
The base case  is if $n=0$ and $m=0$ then 
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
and by rule (2) we have
 \begin{mathpar}
 % \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
For the inductive step, first we have by induction hypothesis that the formula is valid for some length $l$ such that $l=n+m+1$, we have 
\TODO{I will complete}

on other hand by rule (2) we have
\begin{mathpar}
 % \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\tau} s'} \in \WT
}
\end{mathpar}

\noindent ($\Leftarrow$) We proceed also by induction on the depth of the inference of 
\begin{mathpar}
{ \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar}
First, using rule (1) we can directly conclude \\

Second by using rule (2),  
\begin{mathpar}
{ \openrule
         {
          \overline{\gamma} \!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar}
implies that 
\begin{mathpar}
\openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
\end{mathpar}
such that $\overline{\gamma} = \vis{\overline{\beta}}$.\\
Finally by using rule (3) we have
\begin{mathpar}
\inferrule{
\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT
\quad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
\quad
\openrule
         {
           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\!\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}{}
\end{mathpar}
and by induction hypothesis this means that we have first,
\begin{mathpar}
%\inferrule{
\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT

implies

\begin{mathpar}
\forall i \in [0\ldots n_1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         
\end{mathpar}

such that\\
\begin{mathpar} 
s=s^1_0 \wedge s^1_{n_1}=s_1 \quad
\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}} 
\quad
\Pred_1=\bigwedge_{i=0}^{n_1}\Pred^1_i\quad \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1
\end{mathpar}

Secondly,
\begin{mathpar}
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT

\end{mathpar}
implies
\begin{mathpar}
\forall i \in [0\ldots n_2].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\end{mathpar}
such that\\
\begin{mathpar} 
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2
\\\\
\overline{\gamma}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred^3_i\subst{\Post^2})\subst{\Post^1_i}

\end{mathpar}
Finally,
\begin{mathpar}
%\inferrule{
\openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT

implies

\begin{mathpar}
\forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         
\end{mathpar}

such that\\
\begin{mathpar} 
s_2=s^3_0 \wedge s^1_{m_1}=s' \quad
\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}} 
\quad
\Pred_3=\bigwedge_{i=0}^{m_1}\Pred^3_i\quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
\end{mathpar}

------------------------------------------------------

>>>>

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \Longleftrightarrow\\  \Bigg( 
 \Big(\alpha = \tau \wedge  \vis{\overline{\beta^2}}=\emptyset \wedge \Pred\,^2 =\symb{True} \wedge \Post^2 =\symb{Id(s)}\Big) \Bigg) \bigvee  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}
where\\
\begin{mathpar} 
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s', \quad
\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}
\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
\end{mathpar}

\begin{proof} ($\Rightarrow$) We proceed by induction the number of transitions $l$ with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}). We have  $l=n+m+1$.
\begin{itemize}
\item The base case $l=1$ ($n=0$ and $m=0$) then obtain
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule (2) we have
 \begin{mathpar}
 % \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. In particular, for $n+1$ or $m+1$.

First by using rule (2) (and by replacing $\alpha$ by $\tau$)  we can directly conclude :
\begin{mathpar}
 % \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\tau} s'} \in \WT
}
\end{mathpar}

Second by using rule (3) \TODO{To complete}

\end{itemize}
\noindent ($\Leftarrow$) We proceed also  by induction the number of transitions $l$ with which we  build  a weak transition.

\begin{itemize}
\item Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:

\begin{mathpar}
{ \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar}
W have two cases:
\begin{itemize}
\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. \TODO{Conclusion?}

\item Or we can directly conclude by rule (2) that we have
\begin{mathpar}
\openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
\end{mathpar}
such that $\overline{\gamma} = \vis{\overline{\beta}}$
\end{itemize}
\item Step: by using rule (3) we can rewrite a weak transition:

\begin{mathpar}
{ \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar}

as

\begin{mathpar}
\inferrule{
\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT
\quad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
\quad
\openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3 }
         {s_2 \OTWeakarrow {\tau} s'} \in\!\WT
%\\
%\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}{}
\end{mathpar}

such that \\
$\overline{\gamma}=\overline{\gamma_1} \dotcup \overline{\gamma_2} \dotcup \overline{\gamma_3}$, 
$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post=$ \\

By induction hypothesis and simplification we have: \\

\begin{mathpar}
%\inferrule{
\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT

\Rightarrow

\forall i \in [0\ldots n_1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         
\end{mathpar}

where 
\begin{mathpar} 
s=s^1_0 \wedge s^1_{n_1}=s_1 \quad
\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}} 
\quad
\Pred_1=\bigwedge_{i=0}^{n_1}\Pred^1_i\quad \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1
\end{mathpar}

and

\begin{mathpar}
%\inferrule{
\openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT

\Rightarrow

\forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         
\end{mathpar}
where

\begin{mathpar} 
s_2=s^3_0 \wedge s^1_{m_1}=s' \quad
\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}} 
\quad
\Pred_3=\bigwedge_{i=0}^{m_1}\Pred^3_i\quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
\end{mathpar}

and

\begin{mathpar}
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT

\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
\begin{mathpar} 
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2
\\\\
\overline{\gamma}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred^3_i\subst{\Post^2})\subst{\Post^1_i}

@@
